A Lyapunov Analysis of Momentum Methods \\ in Optimization

### 2016-10-24 LyapDraft.tex
edited abstract a bit. made some small changes

\begin{document}
\title{A Lyapunov Analysis of Momentum Methods \\ in  Optimization}
%\title{A Lyapunov Perspective on Momentum Methods \\ in  Optimization}
\date{}
\author{Ashia C. Wilson \and Benjamin Recht \and Michael I. Jordan}
\maketitle
\begin{abstract}
Momentum methods play a central role in convex optimization. Several momentum methods are provably optimal and all use a technique called {\em estimate sequences} to analyze their behavior.  The technique of estimate sequences has long been considered difficult to understand. In the following paper, we show there is an equivalence between the technique of estimate sequences and a family of Lyapunov functions in both continuous and discrete-time. This framework allows us to develop a simplified and unified analysis of several existing algorithms, introduce a couple of interesting new methods, and deepens the connection between algorithms and differential equations. 
\end{abstract}

@@

 \frac{d}{dt} \nabla h(Z_t) &= -\left(\frac{d}{dt}e^{\beta_t}\right) \nabla f(X_t). \label{Eq:X}

@@

A_{k+1} \phi_{k+1} \leq A_k \phi_k + (A_{k+1} - A_k) f(x)\\

@@

\phi_{k} &\leq \Big(1 -\frac{A_0}{A_k}\Big) f(x) + \frac{A_0}{A_k} \phi_0(x)\\
& =  \Big(1 -\frac{1}{A_k}\Big) f(x) + \frac{1}{A_k} \phi_0(x)\\

>>>>

\begin{document}
\title{A Lyapunov Analysis of Momentum Methods \\ in  Optimization}
%\title{A Lyapunov Perspective on Momentum Methods \\ in  Optimization}
\date{}
\author{Ashia C. Wilson \and Benjamin Recht \and Michael I. Jordan}
\maketitle
\begin{abstract}
Momentum methods play a central role in convex optimization. Several momentum methods are provably optimal and all use a technique called {\em estimate sequences} to analyze their behavior.  The technique of estimate sequences has long been considered difficult to understand. In the following paper, we show there is an equivalence between the technique of estimate sequences and a family of Lyapunov functions in both continuous and discrete time. This framework allows us to develop a simplified and unified analysis of several existing algorithms, introduce a couple of interesting new algorithms. Furthermore, it strengthens the connection between algorithms and continuous time dynamical systems . 
\end{abstract}

@@

 \frac{d}{dt} \nabla h(Z_t) &= -\frac{d}{dt}\left(e^{\beta_t}\right) \nabla f(X_t). \label{Eq:X}

@@

A_{k+1} \phi_{k+1} &\leq A_k \phi_k + (A_{k+1} - A_k) f(x)

@@

\phi_{k+1} &\leq \Big(1 -\frac{A_0}{A_{k+1}}\Big) f(x) + \frac{A_0}{A_{k+1}} \phi_0(x)\\
& =  \Big(1 -\frac{1}{A_{k+1}}\Big) f(x) + \frac{1}{A_{k+1}} \phi_0(x)\\
